\LARGE \bf Cross Validation of Emotional Features with a non-Anthropomorphic Platform

### 2017-03-23 RO-MAN-2017-1/Parts/Results.tex
Update Results.tex

It could be observed that both implementations of \textit{Happiness} were confused with \textit{Anger} and \textit{Excitement}. In a similar way, \textit{Anger-1} was mostly confused with \textit{Excitement}, which was voted twenty one over forty nine subjects.
\textit{Anger-2} shows an improvement of perception from 10\% to 38\% with respect to Anger-1. This implementation was perceived also as \textit{Happiness}, \textit{Fear} and \textit{Excitement}.
Both implementations of \textit{Fear} had a high level of recognition, respectively 54\% and 50\%, although they have been mostly confused with \textit{Excitement}, which was voted nine times for the first implementation and twenty times for the second implementation. Finally, the two implementation of \textit{Sadness} were confused with \textit{Fear} and \textit{Tenderness}.

An analysis was done per groups, for each presented emotion. For each emotion, it was considered how many subjects presented with that emotion expression recognized it, how many of those identified a different emotion, how many identified the considered emotion when presented another one, and how many subjects recognized an emotion different from the considered one when presented a different emotion. This lead to a contingency table, for each presented emotion, like the one reported in table~\ref{table:singleEmotion} for Happiness-1. 
\begin{table}[!htbp]
\begin{center}
\caption{Example of table compiled for each emotion on the subjects which have been presented each emotion (here Happiness-1).}
\label{table:singleEmotion}
\begin{tabular}{|c|c|c|}
\hline 
Presented/Reported&Happiness&Other\\
\hline 
Happiness-1&8&54\\
\hline 
Other&42&355\\
\hline
\end{tabular}
\end{center}
%\vspace{-0.5cm}
\end{table}

@@

Additionally, the positive predictive value, accuracy and a Pearson's $\chi^2$ were computed for each table. The hypothesis used in the test were:

@@

Nevertheless, it is important to notice that the results were obtained using the lower part of the robot without any change in its shape. Another important factor to highlight is the impact that the words listed in the questionnaire have on the perception rate. As it was expected, mental states \textit{Excitement} and \textit{Tenderness} were confused with emotions with similar arousal level. In this precise case the emotions \textit{Anger}, \textit{Happiness}, and \textit{Fear} were confused with\textit{Excitement}, and \textit{Sadness} was confused with \textit{Tenderness}. Despite the bias generated by the two mental states listed in the questionnaire, the recognition rate of five out of eight implementations was over 35\%, being the two implementations of \textit{Fear} the implementations with the higher recognition rates (54\% for the first and 50\% for the second).

@@

The results obtained from the scene trials are presented in Table~\ref{table:preference_selection}. From this data, two questions had to be answered:
\begin{enumerate}
	\item Do people prefer scenes with or without emotions?
	\item Has gender an impact in the preference?
\end{enumerate}
To answer these questions the following hypotheses were created:
\begin{enumerate}
	\item $H_0 =$ there is a preference towards scenes with emotions. $H_1$ there is a preference towards scenes without emotions. 
	\item $H_0 =$ there is an association between gender and the preference. $H_1 =$ there is not an association between gender and the preference. 
\end{enumerate}
A $\chi^2$ test with one degree of freedom and $\alpha = 0.05$ was done to verify them. The results of the tests show that there is enough statistical evidence to accept that people prefer scenes with emotions ($p<0.001$). On the other hand, the test shows that there is no association between gender and preference $(p=0.85)$.

>>>>

It could be observed that both implementations of \textit{Happiness} were confused with \textit{Anger} and \textit{Excitement}. In a similar way, \textit{Anger-1} was mostly confused with \textit{Excitement}, which was voted twenty one times by forty nine subjects exposed to it.
\textit{Anger-2} shows an improvement of perception from 10\% to 38\% with respect to Anger-1. This implementation was perceived also as \textit{Happiness}, \textit{Fear} and \textit{Excitement}.
Both implementations of \textit{Fear} had a high level of recognition, respectively 54\% and 50\%, although they have been mostly confused with \textit{Excitement}, which was voted nine times for the first implementation and twenty times for the second implementation. Finally, the two implementation of \textit{Sadness} were confused with \textit{Fear} and \textit{Tenderness}.

An analysis was done per groups, for each presented emotion. For each emotion, it was considered how many subjects presented with that emotion expression recognized it, how many identified a different emotion, how many identified the considered emotion when presented another one, and how many subjects recognized an emotion different from the considered one when presented a different emotion. This leads to a contingency table, for each presented emotion, like the one reported in table~\ref{table:singleEmotion} for Happiness-1. 
\begin{table}[!htbp]
\begin{center}
\caption{Example of table compiled for each emotion on the subjects which have been presented each emotion (here Happiness-1).}
\label{table:singleEmotion}
\begin{tabular}{|c|c|c|}
\hline 
Presented/Reported&Happiness&Other\\
\hline 
Happiness-1&8&54\\
\hline 
Other&42&355\\
\hline
\end{tabular}
\end{center}
%\vspace{-0.5cm}
\end{table}

@@

Additionally, the positive predictive value, accuracy and a Pearson's $\chi^2$ were computed for each table. The hypotheses used in the test were:

@@

Nevertheless, it is important to notice that the results were obtained using the lower part of the robot without any change in its shape. Another important factor to highlight is the impact that the words listed in the questionnaire have on the perception rate. As it was expected, mental states \textit{Excitement} and \textit{Tenderness} were confused with emotions with similar arousal level. In this precise case, the emotions \textit{Anger}, \textit{Happiness}, and \textit{Fear} were confused with\textit{Excitement}, and \textit{Sadness} was confused with \textit{Tenderness}. Despite the bias generated by the two mental states listed in the questionnaire, the recognition rate of five out of eight implementations was over 35\%, being the two implementations of \textit{Fear} the implementations with the higher recognition rates (54\% for the first and 50\% for the second).

@@

The results obtained from the scene trials are presented in Table~\ref{table:preference_selection}. From this data, two questions had to be answered:
\begin{enumerate}
	\item Do people prefer scenes with or without emotions?
	\item Has gender an impact on the preference?
\end{enumerate}
To answer these questions the following hypotheses were considered:
\begin{enumerate}
	\item $H_0 =$ there is a preference towards scenes with emotions. $H_1$ there is a preference towards scenes without emotions. 
	\item $H_0 =$ there is an association between gender and the preference. $H_1 =$ there is not an association between gender and the preference. 
\end{enumerate}
A $\chi^2$ test with one degree of freedom and $\alpha = 0.05$ was done to verify them. The results of the tests show that there is enough statistical evidence to accept that people prefer scenes with emotions ($p<0.001$). On the other hand, the test shows that there is no association between gender and preference $(p=0.85)$.
